---
title: "Homework 1"
author: "luyao mao"
date: "2026-09-26"
output: github_document
---

## Library

```{r}
library("tidyverse")
```

## Problem 1

```{r}
data("penguins", package = "palmerpenguins")
```

The penguins dataset has information about different penguins, with variables including `r paste(names(penguins), collapse = ", ")`. The three species are `r paste(levels(penguins$species), collapse = ", ")` and the penguins are from `r paste(levels(penguins$island), collapse = ", ")` islands.

The size of this dataset are `r nrow(penguins)` observations and `r ncol(penguins)` variables.

The mean of flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)`.

```{r warning=FALSE}
plot_df = 
  tibble( x = penguins$bill_length_mm, 
          y = penguins$flipper_length_mm )

ggplot( plot_df, 
        aes( x = x, y = y, color = penguins$species )) + geom_point()

ggsave( filename = "penguins_scatterplot.png" )
```

## Problem 2

### Create a dataframe

```{r}
set.seed(1)

problem2_df = 
  tibble( num_var = rnorm(10),
          log_var = num_var > 0,
          cha_var = letters[1:10],
          fac_var = factor( rep(c("A", "B", "C"), length.out = 10 ))
  )

problem2_df
```

### Take the mean of each variable

```{r}
mean(pull(problem2_df, num_var))
mean(pull(problem2_df, log_var))
mean(pull(problem2_df, cha_var))
mean(pull(problem2_df, fac_var))
```

The mean works for the numeric and logical variables. It does not work for the character and factor variables. R returns `NA` because these variables are not numeric or logical.

### Convert variables from one type to another

```{r eval = FALSE, warning=FALSE}
as.numeric(pull(problem2_df, log_var))
as.numeric(pull(problem2_df, cha_var))
as.numeric(pull(problem2_df, fac_var))
```

After using `as.numeric`, the logical variable changes to 0 and 1 because R treats `FALSE` as 0 and `TRUE` as 1. 
The character variable changes to `NA` because letters cannot be converted to numbers. The factor variable changes to 1, 2, and 3. These numbers are the internal codes for the three factor levels, not actual numerical measurements.
This explains why the mean works for the logical variable. Its mean is the proportion of `TRUE` values. The mean does not work for the character variable because its values are not numbers. The factor variable represents categories, so taking the mean of its level codes is not meaningful.
