---
title: "Homework 1"
author: "luyao mao"
date: "2026-09-26"
output: github_document
---

## Library

```{r}
library("tidyverse")
```

## Problem 1

```{r}
data("penguins", package = "palmerpenguins")
```

The penguins dataset has information about different penguins, with variables including `r paste(names(penguins), collapse = ", ")`. The three species are `r paste(levels(penguins$species), collapse = ", ")` and the penguins are from `r paste(levels(penguins$island), collapse = ", ")` islands.

The size of this dataset are `r nrow(penguins)` observations and `r ncol(penguins)` variables.

The mean of flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)`.

```{r warning=FALSE}
plot_df = 
  tibble( x = penguins$bill_length_mm, 
          y = penguins$flipper_length_mm )

ggplot( plot_df, 
        aes( x = x, y = y, color = penguins$species )) + geom_point()

ggsave( filename = "penguins_scatterplot.png" )
```

## Problem 2

Create a dataframe

```{r}
set.seed(1)

problem2_df = 
  tibble( num_var = rnorm(10),
          log_var = num_var > 0,
          cha_var = letters[1:10],
          fac_var = factor( rep(c("A", "B", "C"), length.out = 10 ))
  )

problem2_df
```

Take the mean of each variable

```{r}
mean(pull(problem2_df, num_var))
mean(pull(problem2_df, log_var))
mean(pull(problem2_df, cha_var))
mean(pull(problem2_df, fac_var))
```

The mean works for the numeric and logical variables. It does not work for the character and factor variables. R returns `NA` because these variables are not numeric or logical.



